Hierarchical Dispatching and Overriding

### 2017-09-04 NewVersion/paper.tex
new

This paper presents a new model \name{} 
(short for \emph{\textbf{F}eatherweight \textbf{H}ierarchical \textbf{J}ava}) 
that deals with unintentional
method conflicts. In our new model, conflicting methods arising
from unrelated methods can coexist in the same component. Moreover, they
can be \emph{independently overridden}. What ensures unambiguity 
is the use of information about the class hierarchy. In turn, 
hierarchical information is also employed in method dispatching, which 
uses a combination of static and dynamic type information to choose 
the implementation of a method at run-time. We give illustrative 
examples of our language and features and formalize \name{} as a minimal 
Featherweight-Java style calculus.

>>>>

This paper presents a new model \name{} (short for \emph{\textbf{F}eatherweight \textbf{H}ierarchical \textbf{J}ava}) as an extension/variation to the trait model that deals with unintentional method conflicts. The method resolution semantics resembles C++, so part of our formalization can be used as a partial C++ method lookup algorithm formalization. We discuss the similarities and differences with C++ and also advantages and disadvantages. In our new model, conflicting methods arising from unrelated methods can coexist in the same component. Moreover, one novel feature we add to our model is hierarchical method overriding: methods can be \emph{independently overridden} along multiple inheritance hierarchy. What ensures unambiguity is the use of information about the class hierarchy. In turn, hierarchical information is also employed in method dispatching, which uses a combination of static and dynamic type information to choose the implementation of a method at run-time. We give illustrative examples of our language and features and formalize \name{} as a minimal Featherweight-Java style calculus.

### 2017-09-04 NewVersion/sections/Introduction.tex
new

As Cook~\cite{Cook1987} put it, 
``\emph{multiple inheritance is good but there is no good way to do it}'', 
that is one reason why many programming languages refuse to support multiple
inheritance in the past.
One of the most sensitive and critical issues is perhaps the ambiguity
introduced by multiple inheritance. One case is the famous
\textit{diamond problem}~\cite{Sak89dis,Singh1995} (also known as ``fork-join inheritance''~\cite{Sak89dis}). 
In the diamond problem, inheritance could allow
one feature to be inherited from multiple parent classes that share a
common ancestor, hence
conflicts arise. The variety of strategies for resolving such conflicts
urges the occurrence of different multiple inheritance models,
including traits, mixins, CZ~\cite{malayeri2009cz}, and many others. Existing
languages and research have taken care of this case extensively. Other issues
including how multiple inheritance deals with state, 
have also been discussed quite extensively~\cite{classless,malayeri2009cz,stroustrup1995}.

>>>>

A reason why programming languages have resisted to multiple
inheritance in the past is that, as Cook~\cite{Cook1987} puts it, 
``\emph{multiple inheritance is good but there is no good way to do it}''.
One of the most sensitive and critical issues is perhaps the ambiguity
introduced by multiple inheritance. One case is the famous
\textit{diamond problem}~\cite{Sak89dis,Singh1995} (also known as ``fork-join inheritance''~\cite{Sak89dis}). 
In the diamond problem, inheritance could allow
one feature to be inherited from multiple parent classes that share a
common ancestor, hence
conflicts arise. The variety of strategies for resolving such conflicts
urges the occurrence of different multiple inheritance models,
including traits, mixins, CZ~\cite{malayeri2009cz}, and many others. Existing
languages and research have taken care of this case extensively. Other issues
including how multiple inheritance deals with state, 
have also been discussed quite extensively~\cite{classless,malayeri2009cz,stroustrup1995}.
